A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-10 docs/methods/erosion_methods.tex
added references to conclusions

As a longer term goal, we would like to include the effect of sedimentation to more faithfully capture the physics of a porous medium. Sedimentation requires overcoming a few challenges. First, the bodies must be mobile, as has been accomplished in previous work (cite). Second, contacts and overlap between bodies must be prevented. This second requirement has been recognized as quite a challenge, with many novel methods developed to treat it (CITE STUFF HERE). Incorporation of one or more of these schemes, will enable simulations of a porous medium undergoing simultaneous erosion and sedimentation.

>>>>

As a longer term goal, we would like to include the effect of sedimentation to more faithfully capture the physics of a porous medium. Sedimentation requires overcoming a few challenges. First, the bodies must be mobile, as has been accomplished in previous work for dense concentrations of deformable and rigid bodies~\cite{qua-bir2014a, cor-gre-rac-vee2017, cor-vee2017, kli-tor2016b, rac-gre2016}. Second, contacts and overlap between bodies must be prevented. This second requirement has been recognized as quite a challenge, with many novel methods developed to treat it~\cite{lu-rah-zor2017, kab-qua-bir2018, san-mo1994}. Incorporation of one or more of these schemes, will enable simulations of a porous medium undergoing simultaneous erosion and sedimentation.
